Investigate relations in incomplete datasets to inform imputation model

### 2020-02-18 3.Thesis/inspect_incomplete_data.Rmd
created density plots for all continuous variables vs. the missingness indictors

# this works for the lm, but not yet for the intercep-only model
#all_interc_only <- cont_vars %>% map(~lm(dat[,.x] ~ 1))
# test2 <- map(cont_vars, function(x) map(vars, function(y) lm(dat[,x]~is.na(dat[,y])) %>% anova(interc_only[[x]], .)))
# map(test, function(x) map(interc_only, function(y) anova(y,x)))
test <- map(cont_vars, function(x) map(vars, function(y) {anova(lm(dat[,x]~1), lm(dat[,x]~is.na(dat[,y])))}))

>>>>

# this works for the lm, but not yet for the intercep-only model
#all_interc_only <- cont_vars %>% map(~lm(dat[,.x] ~ 1))
# test2 <- map(cont_vars, function(x) map(vars, function(y) lm(dat[,x]~is.na(dat[,y])) %>% anova(interc_only[[x]], .)))
# map(test, function(x) map(interc_only, function(y) anova(y,x)))
test2 <- map(cont_vars, function(x) map(vars, function(y) {anova(lm(dat[,x]~1), lm(dat[,x]~is.na(dat[,y])))}))

```
 Ok, I think this works. Now get it to work for the density plots.

```{r}
# create density plots for all continuous variables and all missingness indicators
test <- map(cont_vars, function(x) map(vars, function(y) lm(dat[,x]~is.na(dat[,y]))))

plots <- map(cont_vars, function(x) map(vars, function(z) {ggplot(data = dat, aes(x = dat[,x], fill = is.na(dat[,z]))) +
  geom_histogram(alpha = 0.5, position = 'identity') +
  xlab(paste0(x)) +
  ylab("number of cases") +
  scale_fill_manual(
    name = z,
    breaks = c("FALSE", "TRUE"),
    labels = c("observed", "missing"),
    values = c("#006CC2", "#B61A51")
  )
  }))
